\\fontsize{12pt}{3pt}\\selectfont \\textbf{\\textit{Journal: Ecosphere. Manuscript ID: ECS23-0342. Manuscript type: Article}}

### 2024-02-12 manuscript/manuscriptRW.Rmd
update gitignore
change Paola's affiliation

- Daniel Scherrer$^{16}$,

@@

       $^6 Department of Ecological Modelling, Helmholtz-Centre for Environmental Research - UFZ, Permoserstraße 15, 04318 Leipzig, Germany. \newline

@@

       $^9$Department of Soil Sciences, of Plants and Food, University of Bari Aldo Moro, Italy. \newline

>>>>

- Daniel Scherrer$^{17}$,

@@

       $^6$Department of Ecological Modelling, Helmholtz-Centre for Environmental Research - UFZ, Permoserstraße 15, 04318 Leipzig, Germany. \newline

@@

       $^9$Dipartimento di Scienze del suolo, della pianta e degli alimenti Università degli Studi di Bari Aldo Moro via Amendola 165/A, 70126 Bari, Italy \newline
